---
title: "Lab4Package"
authors: Marketos Damigos (marda352) & Christoforos Spyretos (chrsp415)
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab4Package}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---



```{r, include = FALSE}

library(ggplot2)

library(linear.regression)

```

##  Introduction

Implementation of Linear Regression with QR Decomposition in R-language using RC-class by Marketos Damigos (marda352) and Christoforos Spyretos (chrsp415).

##  Usage Methods

```{r echo=TRUE, fig.show='hold'}

linear_regression = linreg(Petal.Length~Species, data=iris)

```

###  print()

The print() function calls the formula along with the coefficients.

```{r, fig.show='hold'}

linear_regression$print()

```

###  plot()

The plot() function returns the plots of Residuals vs Fitted Values and Scale Location.

```{r}

linear_regression$plot()

```

###  resid()

The resid() function returns the residuals values.
$$\hat{e} = y - \hat{y} = y - X\hat{\beta}$$

```{r, fig.show='hold', fig.align='center'}

head(linear_regression$resid())

```

###  pred()

The pred() function retyrns the predicted values. 
$$\hat{y}$$

```{r, fig.show='hold'}

head(linear_regression$pred())

```

###  coef()

The coef() function returns the coefficients values, $$\hat{\beta} = (X^TX)^{-1}X^Ty$$

```{r, fig.show='hold'}

linear_regression$coef()

```

###  summary()

The summary() function returns coefficients values with their standard error, t-value, p-value as well as the estimate of $\hat{\sigma}$ along with the degrees of freedom.

```{r, fig.show='hold'}

linear_regression$summary()

```
##  References
[Matrix decompositions for regression analysis](https://www.stat.wisc.edu/courses/st849-bates/lectures/Orthogonal.pdf)
[Wikipedia Linear Regression](https://en.wikipedia.org/wiki/Linear_regression)
